---
title: "Activity 7 - Linear Discriminant Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
```

## Task 3

```{r load data}
resume <- readr::read_csv("https://www.openintro.org/data/csv/resume.csv")
```
## Question 1: The plot on the right satisfies the assumption. The plot on the left is skewed right while the plot on the right is a normal distribution. 

## Task 4

```{r}
# Convert received_callback to a factor with more informative labels
resume <- resume %>% 
  mutate(received_callback = factor(received_callback, labels = c("No", "Yes")))

# LDA
library(discrim)
lda_years <- discrim_linear() %>% 
  set_mode("classification") %>% 
  set_engine("MASS") %>% 
  fit(received_callback ~ log(years_experience), data = resume)

lda_years
```
## Question 2
The values for Group Means for yes and no are pretty similar.


## Question 3
The peaks for received_callback yes and no are at the locations for the group means of yes and no. 


## Task 5

```{r generating predictions}
predict(lda_years, new_data = resume, type = "prob")
```

```{r creating confusion matrix}
augment(lda_years, new_data = resume) %>% 
  conf_mat(truth = received_callback, estimate = .pred_class)

```

## Question 4
The model never predicted yes. I think it happened because it is very uncommon to receive a callback so it did not predict it. 

```{r}
augment(lda_years, new_data = resume) %>% 
  accuracy(truth = received_callback, estimate = .pred_class)
```

